A New Method of Modelling Tuneable Lasers with Functional Composition

### 2020-11-15 Papers/Journal/Tuneable_Lasers.tex
Added conclusion

\section{Conclusion}
\label{sec:conclusion}

\section{Acknowledgement}
BM acknowledges the support provided by the EPSRC Centre for Doctoral Training in Industrially Focused Mathematical Modelling (EP/L015803/1).

>>>>

\section{Conclusion}
\label{sec:conclusion}
Expanding upon the ideas originally proposed by Cutler \cite{cutler1955}, and Kuizenga and Siegman \cite{kuizenga1970, kuizenga1970a, siegman1969}, we developed a nonlinear functional model for tuneable ring lasers. We recover linearly chirped Gaussian solutions in the case of a Gaussian modulation function when omitting the nonlinearity. Moreover, the solution of the linear model can easily be extended to any modulation function using results of \cite{calcaterra2008a}. In contrast, with the inclusion of the nonlinearity we were able to recover wave breaking and modulation instability, and found a sharp boundary of stability. This phenomenon has been demonstrated in a laboratory setting \cite{agrawal2013, anderson1992, finot2008, rothenberg1989b, tomlinson1985}, but, has difficult to predict with mathematical models. Furthermore, it is of interest to analyze the nonlinear model analytically using an asymptotic expansion for small values of the nonlinearity parameter, $b$. Doing so would provide insight to how the nonlinearity impacts the linearized solution to better understand the manifestation of wave breaking and modulation instability.

\section*{Acknowledgement.}
BM acknowledges the support provided by the EPSRC Centre for Doctoral Training in Industrially Focused Mathematical Modelling (EP/L015803/1).

\section*{Disclosures.}
The authors declare no conflicts of interest.
